### 2025-06-06 sec/introduction.tex
[update] padding for listing

\lstset{
    aboveskip=-2.3pt,    % riduce lo spazio sopra
    belowskip=-2pt,    % riduce lo spazio sotto
    xleftmargin=0pt,   % riduce il margine sinistro
    xrightmargin=0pt   % riduce il margine destro
}

@@

\begin{table}[!ht]
    \centering
    \footnotesize
    \renewcommand{\arraystretch}{0.9}
    \begin{tabular}{>{\raggedright\arraybackslash}p{2cm} >{\raggedright\arraybackslash}p{5cm} >{\raggedright\arraybackslash}p{6cm}}
        \toprule
        \textbf{Type}                & \textbf{Example} & \textbf{Generated Expression} \\
        \midrule
        \rowcolor{gray!20}
        \multicolumn{3}{>{\raggedright\arraybackslash}l}{\textbf{Quantitative expressions}} \\

@@

        \end{lstlisting}  \\
        Rounding & ~                & ~                             \\
        Cardinals \& Multiplicative & ~                & ~                             \\
        \rowcolor{gray!20}
        \multicolumn{3}{>{\raggedright\arraybackslash}l}{\textbf{Aggregation}} \\
        Average
        & The average methane emissions for the year 2030 is \hl{13.51} &
        %\vspace{-8pt}
        \begin{lstlisting}[language=Fluid,numbers=none]
(sumEmissions year tableData / length records)
        \end{lstlisting} \\
        Min/Max                          & The Energy Sector recorded its highest methane emissions in \hl{2030}             &
        %\vspace{-8pt}
        \begin{lstlisting}[language=Fluid,numbers=none]
let maxEntry =
    maximumBy (fun x -> x.emissions)
              (filter
                (fun x -> x.type == "Energy Sector")
                tableData)
in maxEntry.year
        \end{lstlisting} \\
        Ranks &
        3-layer stacked CNN gives an accuracy of 81.46\%, which is the \hl{lowest} compared with BiLSTM, and S-LSTM  &
        %\vspace{-10pt}
        \begin{lstlisting}[language=Fluid,numbers=none]
let pos =
  findIndex "model" "CNN"
    (insertionSort cmpTime tableData)
in rankLabel "lowest" pos
        \end{lstlisting} \\
        Total &
        The total methane emissions for the year 2030 is \hl{37.74} for Agriculture &
        %\vspace{-8pt}
        \begin{lstlisting}[language=Fluid,numbers=none]
sumEmissions year tableData
        \end{lstlisting} \\
        Count*                       & ~                & ~                             \\
        \rowcolor{gray!20}
        \multicolumn{3}{>{\raggedright\arraybackslash}l}{\textbf{Trends}} \\

>>>>

\lstset{
    aboveskip=-7pt,
    belowskip=-8.5pt,
    xleftmargin=0pt,
    xrightmargin=0pt
}

@@

\begin{table}[!ht]
    \centering
    \footnotesize
    \renewcommand{\arraystretch}{1.0}
    \begin{tabular}{>{\raggedright\arraybackslash}p{2cm} >{\raggedright\arraybackslash}p{5cm} >{\raggedright\arraybackslash}p{6cm}}
        \toprule
        \textbf{Type}                & \textbf{Example} & \textbf{Generated Expression} \\
        \rowcolor{gray!20}
        \multicolumn{3}{>{\raggedright\arraybackslash}l}{\textbf{Quantitative expressions}} \\

@@

        \end{lstlisting}  \\
        Rounding & ~                & ~                             \\
        Cardinals \& Multiplicative & ~                & ~                             \\
        \rowcolor{gray!20}
        \multicolumn{3}{>{\raggedright\arraybackslash}l}{\textbf{Aggregation}} \\
        Average
        & The average methane emissions for the year 2030 is \hl{13.51} &
        %\vspace{-8pt}
        \begin{lstlisting}[language=Fluid,numbers=none]
(sumEmissions year tableData / length records)
        \end{lstlisting} \\
        Min/Max                          & The Energy Sector recorded its highest methane emissions in \hl{2030}             &
        %\vspace{-8pt}
        \begin{lstlisting}[language=Fluid,numbers=none]
let maxEntry =
    maximumBy (fun x -> x.emissions)
              (filter
                (fun x -> x.type == "Energy Sector")
                tableData)
in maxEntry.year
        \end{lstlisting} \\
        Ranks &
        3-layer stacked CNN gives an accuracy of 81.46\%, which is the \hl{lowest} compared with BiLSTM, and S-LSTM  &
%        \vspace{-15pt}
        \begin{lstlisting}[language=Fluid,numbers=none]
let pos =
  findIndex "model" "CNN"
    (insertionSort cmpTime tableData)
in rankLabel "lowest" pos \end{lstlisting} \\\hline
        Total &
        The total methane emissions for the year 2030 is \hl{37.74} for Agriculture &
        %\vspace{-8pt}
        \begin{lstlisting}[language=Fluid,numbers=none]
sumEmissions year tableData
        \end{lstlisting} \\
        Count*                       & ~                & ~                             \\
        \rowcolor{gray!20}
        \multicolumn{3}{>{\raggedright\arraybackslash}l}{\textbf{Trends}} \\
